Data Management \\ and LSST Special Programs

### 2021-11-27 DMTN-065.tex
updated camera rotation as per DM-12573

{\bf Camera Rotation -- } There requirements on the rotator's capabilities do not set any limits on the per-night or total lifetime rotation (OSS-REQ-0301, -0300; \citeds{LSE-30}) which might put boundaries on the distance between successive visits or the ability to jump between two widely separated fields. JIRA ticket DM-12573 is currently open and asking for clarification from the camera team on this. Until then, we assume there are no technical boundaries imposed by camera rotation constraints on the potential diversity of data products.

>>>>

{\bf Camera Rotation -- } There requirements on the rotator's capabilities do not set any limits on the per-night or total lifetime rotation (OSS-REQ-0301, -0300; \citeds{LSE-30}) which might put boundaries on the distance between successive visits or the ability to jump between two widely separated fields.
Currently, there are no technical boundaries imposed by camera rotation constraints on the potential diversity of data products.
